The Skew-Normal Approximation of the Binomial Distribution

### 2010-12-19 pieces/final-paper/output.tex
Tweaks.

\begin{equation} \label{eq:standard-sn-pdf}
  f_z(x) = 2 \cdot \phi(x) \cdot \Phi (\lambda x)
\end{equation}

Similar to the normal and standard normal, $X = \frac{Y - \mu}{\sigma}$ and $Y
= \sigma X + \mu$.

@@

\begin{align*}
  f_Y(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
  &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
  &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
  &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
  &= \frac{1}{\sqrt{2\pi\sigma^2}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right)
\end{align*}

@@

  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_z(z) = 2 \cdot \phi(z) \cdot
  \Phi(\lambda z)$ conforms to equation
  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $phi$
  and $Z$ are equal in distribution.

%  Notice that $\phi(x)$ is a one-dimensional probability density function
%  symmetric about 0, and $\Phi(x)$ is a one-dimensional distribution function
%  such that $\Phi'$ exists and is a density symmetric about 0. Furthermore,
%  $\lambda x$ is an odd function. Thus, $f_z(z) = 2 \cdot \phi(z) \cdot
%  \Phi(\lambda z)$ conforms to equation
%  \eqref{eq:azzalini-perturbation-invariance}. With that in mind, the corollary
%  to this lemma provides a very useful result:

@@

Now we set the two sets of moments equal to each other and, taking $n$ and $p$
as constants, solve for $\mu$, $\sigma$ and $\lambda$.

@@

Similarly, with both $\lambda$ and $\sigma$, a simple rearrangement of
\eqref{eq:first-moment-set} yields $\mu$:

@@

Another more numerical method would be to compare the maximal absolute errors
of our two approximations, defined by \citet{mabs} as

>>>>

\begin{equation} \label{eq:standard-sn-pdf}
  f_Z(x) = 2 \cdot \phi(x) \cdot \Phi (\lambda x)
\end{equation}

Similar to the normal and standard normal, $Z = \frac{Y - \mu}{\sigma}$ and $Y
= \sigma Z + \mu$.

@@

\begin{align*}
  f_Y(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
  &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
  &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
  &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
  &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right)
\end{align*}

@@

  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_Z(z) = 2 \cdot \phi(z) \cdot
  \Phi(\lambda z)$ conforms to equation
  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $phi$
  and $Z$ are equal in distribution.

%  Notice that $\phi(x)$ is a one-dimensional probability density function
%  symmetric about 0, and $\Phi(x)$ is a one-dimensional distribution function
%  such that $\Phi'$ exists and is a density symmetric about 0. Furthermore,
%  $\lambda x$ is an odd function. Thus, $f_Z(z) = 2 \cdot \phi(z) \cdot
%  \Phi(\lambda z)$ conforms to equation
%  \eqref{eq:azzalini-perturbation-invariance}. With that in mind, the corollary
%  to this lemma provides a very useful result:

@@

Now we can set the moments of our two distributions equal to each other and,
taking $n$ and $p$ as constants, solve for $\mu$, $\sigma$ and $\lambda$.

@@

And with both $\lambda$ and $\sigma$, a simple rearrangement of
\eqref{eq:first-moment-set} yields $\mu$:

@@

A more numerical method would be to compare the maximal absolute errors of our
two approximations, defined by \citet{mabs} as
